CDSR Human Data/Modelling Paper

### 2013-08-10 scenarios/cdsr/trunk/papers/ACS2013/main.tex

\begin{abstract}
Abstract goes here
\end{abstract}

\section{Introduction - KLENK}

\section{Context-Dependent Spatial Regions - KLENK}

\subsection{Explanation of the basic idea}

>>>>

\begin{abstract}
Representing and reasoning about spatial terms is an essential ability for cognitive systems interacting with humans in a shared environment.  Consider a safe area in a military engagement.  The size, shape, and location of this area depend the the capabilities of the other agents and their capabilities in the environment.  We call these regions \textit{context-dependent spatial regions}(CDSRs).  We claim that understanding these regions requires integrating semantic and geometric knowledge about a dynamic environment.  We conducted a human study to explore how people interpret three types of CDSRs that supports the knowledge integration claim.  We evaluate two representation techniques against the human data and discuss their limitations as a cognitive systems solution to this problem.
\end{abstract}

\section{Introduction - KLENK} 
Natural communication between humans and cognitive systems requires both participants to communicate with spatial language.  Many spatial terms are defined not only be their geometry, but also their context.  That is, to understand this language requires considering the other objects and agents in the environment, as well as their configuration and functional roles.  We call such regions \textit{context-dependent spatial regions}(CDSRs).

We begin by discussing CDSRs with examples and two claims about these regions.  Next, we discuss desired properties of a cognitive system solution.  The contribution of this paper is a human study exploring our claims about CDSRs and an empirical exploration of current models and their shortcomings.  We close with a discussion of related and future work.

\section{Context-Dependent Spatial Regions - KLENK}
Consider the following regions: the front of a classroom (\ref{fig:classroom}), safety in military engagement (\ref{fig:safety}), or the geographical feature of a bottleneck (\ref{fig:bottleneck}).  To identify these regions, one must identify the physical boundaries (e.g., walls), the objects within the room and their functional use (e.g., desks oriented toward a whiteboard), and other agent's intentions and capabilities (e.g., enemy tanks can move and have a range of attack).  These regions exists at different levels of spatial resolution.  Consider a neighborhood in a city, whose boundaries expand and contract overtime with changes to the surrounding residents and businesses
